### 2018-03-26 paper/paper.tex
Added basic paper format, copied from NIPS.

\documentclass{article}

% Copy/pasta of nips_2017 for future modification found here:
% https://nips.cc/Conferences/2017/PaperInformation/StyleFiles

% if you need to pass options to natbib, use, e.g.:
% \PassOptionsToPackage{numbers, compress}{natbib}
% before loading nips_2017
%
% to avoid loading the natbib package, add option nonatbib:
% \usepackage[nonatbib]{nips_2017}

\usepackage{nips_2017}

% to compile a camera-ready version, add the [final] option, e.g.:
% \usepackage[final]{nips_2017}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\title{Formatting instructions for NIPS 2017}

% The \author macro works with any number of authors. There are two
% commands used to separate the names and addresses of multiple
% authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to
% break the lines. Using \AND forces a line break at that point. So,
% if LaTeX puts 3 of 4 authors names on the first line, and the last
% on the second line, try using \AND instead of \And before the third
% author name.

\author{
  David S.~Hippocampus\thanks{Use footnote for providing further
    information about author (webpage, alternative
    address)---\emph{not} for acknowledging funding agencies.} \\
  Department of Computer Science\\
  Cranberry-Lemon University\\
  Pittsburgh, PA 15213 \\
  \texttt{hippo@cs.cranberry-lemon.edu} \\
  %% examples of more authors
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

\begin{document}
% \nipsfinalcopy is no longer used

\maketitle

\begin{abstract}
  The abstract paragraph should be indented \nicefrac{1}{2}~inch
  (3~picas) on both the left- and right-hand margins. Use 10~point
  type, with a vertical spacing (leading) of 11~points.  The word
  \textbf{Abstract} must be centered, bold, and in point size 12. Two
  line spaces precede the abstract. The abstract must be limited to
  one paragraph.
\end{abstract}

\section{Submission of papers to NIPS 2017}

NIPS requires electronic submissions.  The electronic submission site
is
\begin{center}
  \url{https://cmt.research.microsoft.com/NIPS2017/}
\end{center}

Please read carefully the instructions below and follow them
faithfully.

\subsection{Style}

Papers to be submitted to NIPS 2017 must be prepared according to the
instructions presented here. Papers may only be up to eight pages
long, including figures. This does not include acknowledgments and 
cited references which are allowed on subsequent pages.
Papers that exceed these limits will not be reviewed, or in any
other way considered for presentation at the conference.

The margins in 2017 are the same as since 2007, which allow for
$\sim$$15\%$ more words in the paper compared to earlier years.

Authors are required to use the NIPS \LaTeX{} style files obtainable
at the NIPS website as indicated below. Please make sure you use the
current files and not previous versions. Tweaking the style files may
be grounds for rejection.

\subsection{Retrieval of style files}

The style files for NIPS and other conference information are
available on the World Wide Web at
\begin{center}
  \url{http://www.nips.cc/}
\end{center}
The file \verb+nips_2017.pdf+ contains these instructions and
illustrates the various formatting requirements your NIPS paper must
satisfy.

The only supported style file for NIPS 2017 is \verb+nips_2017.sty+,
rewritten for \LaTeXe{}.  \textbf{Previous style files for \LaTeX{}
  2.09, Microsoft Word, and RTF are no longer supported!}

The new \LaTeX{} style file contains two optional arguments:
\verb+final+, which creates a camera-ready copy, and \verb+nonatbib+,
which will not load the \verb+natbib+ package for you in case of
package clash.

At submission time, please omit the \verb+final+ option. This will
anonymize your submission and add line numbers to aid review.  Please
do \emph{not} refer to these line numbers in your paper as they will
be removed during generation of camera-ready copies.

The file \verb+nips_2017.tex+ may be used as a ``shell'' for writing
your paper. All you have to do is replace the author, title, abstract,
and text of the paper with your own.

The formatting instructions contained in these style files are
summarized in Sections \ref{gen_inst}, \ref{headings}, and
\ref{others} below.

\section{General formatting instructions}
\label{gen_inst}

The text must be confined within a rectangle 5.5~inches (33~picas)
wide and 9~inches (54~picas) long. The left margin is 1.5~inch
(9~picas).  Use 10~point type with a vertical spacing (leading) of
11~points.  Times New Roman is the preferred typeface throughout, and
will be selected for you by default.  Paragraphs are separated by
\nicefrac{1}{2}~line space (5.5 points), with no indentation.

The paper title should be 17~point, initial caps/lower case, bold,
centered between two horizontal rules. The top rule should be 4~points
thick and the bottom rule should be 1~point thick. Allow
\nicefrac{1}{4}~inch space above and below the title to rules. All
pages should start at 1~inch (6~picas) from the top of the page.

For the final version, authors' names are set in boldface, and each
name is centered above the corresponding address. The lead author's
name is to be listed first (left-most), and the co-authors' names (if
different address) are set to follow. If there is only one co-author,
list both author and co-author side by side.

Please pay special attention to the instructions in Section \ref{others}
regarding figures, tables, acknowledgments, and references.

\section{Headings: first level}
\label{headings}

All headings should be lower case (except for first word and proper
nouns), flush left, and bold.

First-level headings should be in 12-point type.

\subsection{Headings: second level}

Second-level headings should be in 10-point type.

\subsubsection{Headings: third level}

Third-level headings should be in 10-point type.

\paragraph{Paragraphs}

There is also a \verb+\paragraph+ command available, which sets the
heading in bold, flush left, and inline with the text, with the
heading followed by 1\,em of space.

\section{Citations, figures, tables, references}
\label{others}

These instructions apply to everyone.

\subsection{Citations within the text}

The \verb+natbib+ package will be loaded for you by default.
Citations may be author/year or numeric, as long as you maintain
internal consistency.  As to the format of the references themselves,
any style is acceptable as long as it is used consistently.

The documentation for \verb+natbib+ may be found at
\begin{center}
  \url{http://mirrors.ctan.org/macros/latex/contrib/natbib/natnotes.pdf}
\end{center}
Of note is the command \verb+\citet+, which produces citations
appropriate for use in inline text.  For example,
\begin{verbatim}
   \citet{hasselmo} investigated\dots
\end{verbatim}
produces
\begin{quote}
  Hasselmo, et al.\ (1995) investigated\dots
\end{quote}

If you wish to load the \verb+natbib+ package with options, you may
add the following before loading the \verb+nips_2017+ package:
\begin{verbatim}
   \PassOptionsToPackage{options}{natbib}
\end{verbatim}

If \verb+natbib+ clashes with another package you load, you can add
the optional argument \verb+nonatbib+ when loading the style file:
\begin{verbatim}
   \usepackage[nonatbib]{nips_2017}
\end{verbatim}

As submission is double blind, refer to your own published work in the
third person. That is, use ``In the previous work of Jones et
al.\ [4],'' not ``In our previous work [4].'' If you cite your other
papers that are not widely available (e.g., a journal paper under
review), use anonymous author names in the citation, e.g., an author
of the form ``A.\ Anonymous.''

\subsection{Footnotes}

Footnotes should be used sparingly.  If you do require a footnote,
indicate footnotes with a number\footnote{Sample of the first
  footnote.} in the text. Place the footnotes at the bottom of the
page on which they appear.  Precede the footnote with a horizontal
rule of 2~inches (12~picas).

Note that footnotes are properly typeset \emph{after} punctuation
marks.\footnote{As in this example.}

\subsection{Figures}

All artwork must be neat, clean, and legible. Lines should be dark
enough for purposes of reproduction. The figure number and caption
always appear after the figure. Place one line space before the figure
caption and one line space after the figure. The figure caption should
be lower case (except for first word and proper nouns); figures are
numbered consecutively.

You may use color figures.  However, it is best for the figure
captions and the paper body to be legible if the paper is printed in
either black/white or in color.
\begin{figure}[h]
  \centering
  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
  \caption{Sample figure caption.}
\end{figure}

\subsection{Tables}

All tables must be centered, neat, clean and legible.  The table
number and title always appear before the table.  See
Table~\ref{sample-table}.

Place one line space before the table title, one line space after the
table title, and one line space after the table. The table title must
be lower case (except for first word and proper nouns); tables are
numbered consecutively.

Note that publication-quality tables \emph{do not contain vertical
  rules.} We strongly suggest the use of the \verb+booktabs+ package,
which allows for typesetting high-quality, professional tables:
\begin{center}
  \url{https://www.ctan.org/pkg/booktabs}
\end{center}
This package was used to typeset Table~\ref{sample-table}.

\begin{table}[t]
  \caption{Sample table title}
  \label{sample-table}
  \centering
  \begin{tabular}{lll}
    \toprule
    \multicolumn{2}{c}{Part}                   \\
    \cmidrule{1-2}
    Name     & Description     & Size ($\mu$m) \\
    \midrule
    Dendrite & Input terminal  & $\sim$100     \\
    Axon     & Output terminal & $\sim$10      \\
    Soma     & Cell body       & up to $10^6$  \\
    \bottomrule
  \end{tabular}
\end{table}

\section{Final instructions}

Do not change any aspects of the formatting parameters in the style
files.  In particular, do not modify the width or length of the
rectangle the text should fit into, and do not change font sizes
(except perhaps in the \textbf{References} section; see below). Please
note that pages should be numbered.

\section{Preparing PDF files}

Please prepare submission files with paper size ``US Letter,'' and
not, for example, ``A4.''

Fonts were the main cause of problems in the past years. Your PDF file
must only contain Type 1 or Embedded TrueType fonts. Here are a few
instructions to achieve this.

\begin{itemize}

\item You should directly generate PDF files using \verb+pdflatex+.

\item You can check which fonts a PDF files uses.  In Acrobat Reader,
  select the menu Files$>$Document Properties$>$Fonts and select Show
  All Fonts. You can also use the program \verb+pdffonts+ which comes
  with \verb+xpdf+ and is available out-of-the-box on most Linux
  machines.

\item The IEEE has recommendations for generating PDF files whose
  fonts are also acceptable for NIPS. Please see
  \url{http://www.emfield.org/icuwb2010/downloads/IEEE-PDF-SpecV32.pdf}

\item \verb+xfig+ "patterned" shapes are implemented with bitmap
  fonts.  Use "solid" shapes instead.

\item The \verb+\bbold+ package almost always uses bitmap fonts.  You
  should use the equivalent AMS Fonts:
\begin{verbatim}
   \usepackage{amsfonts}
\end{verbatim}
followed by, e.g., \verb+\mathbb{R}+, \verb+\mathbb{N}+, or
\verb+\mathbb{C}+ for $\mathbb{R}$, $\mathbb{N}$ or $\mathbb{C}$.  You
can also use the following workaround for reals, natural and complex:
\begin{verbatim}
   \newcommand{\RR}{I\!\!R} %real numbers
   \newcommand{\Nat}{I\!\!N} %natural numbers
   \newcommand{\CC}{I\!\!\!\!C} %complex numbers
\end{verbatim}
Note that \verb+amsfonts+ is automatically loaded by the
\verb+amssymb+ package.

\end{itemize}

If your file contains type 3 fonts or non embedded TrueType fonts, we
will ask you to fix it.

\subsection{Margins in \LaTeX{}}

Most of the margin problems come from figures positioned by hand using
\verb+\special+ or other commands. We suggest using the command
\verb+\includegraphics+ from the \verb+graphicx+ package. Always
specify the figure width as a multiple of the line width as in the
example below:
\begin{verbatim}
   \usepackage[pdftex]{graphicx} ...
   \includegraphics[width=0.8\linewidth]{myfile.pdf}
\end{verbatim}
See Section 4.4 in the graphics bundle documentation
(\url{http://mirrors.ctan.org/macros/latex/required/graphics/grfguide.pdf})

A number of width problems arise when \LaTeX{} cannot properly
hyphenate a line. Please give LaTeX hyphenation hints using the
\verb+\-+ command when necessary.

\subsubsection*{Acknowledgments}

Use unnumbered third level headings for the acknowledgments. All
acknowledgments go at the end of the paper. Do not include
acknowledgments in the anonymized submission, only in the final paper.

\section*{References}

References follow the acknowledgments. Use unnumbered first-level
heading for the references. Any choice of citation style is acceptable
as long as you are consistent. It is permissible to reduce the font
size to \verb+small+ (9 point) when listing the references. {\bf
  Remember that you can go over 8 pages as long as the subsequent ones contain
  \emph{only} cited references.}
\medskip

\small

[1] Alexander, J.A.\ \& Mozer, M.C.\ (1995) Template-based algorithms
for connectionist rule extraction. In G.\ Tesauro, D.S.\ Touretzky and
T.K.\ Leen (eds.), {\it Advances in Neural Information Processing
  Systems 7}, pp.\ 609--616. Cambridge, MA: MIT Press.

[2] Bower, J.M.\ \& Beeman, D.\ (1995) {\it The Book of GENESIS:
  Exploring Realistic Neural Models with the GEneral NEural SImulation
  System.}  New York: TELOS/Springer--Verlag.

[3] Hasselmo, M.E., Schnell, E.\ \& Barkai, E.\ (1995) Dynamics of
learning and recall at excitatory recurrent synapses and cholinergic
modulation in rat hippocampal region CA3. {\it Journal of
  Neuroscience} {\bf 15}(7):5249-5262.

\end{document}

### 2018-04-19 paper/paper.tex
Cleaned up some of the functions and hyper params. Made main a little more robust. Created ancillary folder to store the things I did to prepare/learn.

@@
 \author{
-  David S.~Hippocampus\thanks{Use footnote for providing further
+  Kyle W.~MacMillan\thanks{Use footnote for providing further
     information about author (webpage, alternative

### 2018-04-19 ancillary/classifier.py

@@ -1,0 +1,105 @@
+
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import argparse
+import os
+import shutil
+import sys
+
+import tensorflow as tf 
+import pandas as pd
+from sklearn.datasets import make_classification
+from sklearn.model_selection import train_test_split
+import numpy as np
+
+
+from input_data import input_fn
+_NUM_CLASSES = 2
+
+# https://github.com/soerendip/Tensorflow-binary-classification/blob/master/Tensorflow-binary-classification-model.ipynb
+def simple_model(in_tensor, num_inputs, num_classes, weights, biases):
+    layer_1 = tf.add(tf.matmul(in_tensor, weights['h1']), biases['b1'])
+    layer_1 = tf.nn.relu(layer_1)
+    layer_2 = tf.add(tf.matmul(layer_1, weights['h2']), biases['b2'])
+    layer_2 = tf.nn.relu(layer_2)
+    layer_3 = tf.add(tf.matmul(layer_2, weights['h3']), biases['b3'])
+    layer_3 = tf.nn.relu(layer_3)
+
+    out_tensor = tf.matmul(layer_3, weights['out']) + biases['out']
+    return out_tensor
+
+
+def main(argv):
+    learning_rate = 0.001
+    num_epochs = 100
+    batch_size = 100 
+    num_hidden_1 = 15
+    num_hidden_2 = 15
+    num_hidden_3 = 15
+
+    num_features = 8
+    X, Y = make_classification(n_samples=50000, n_features=num_features, n_informative=8, 
+                           n_redundant=0, n_clusters_per_class=2)
+    Y = np.array([Y, -(Y-1)]).T  # The model currently needs one column for each class
+    X, X_test, Y, Y_test = train_test_split(X, Y)
+
+    num_inputs = num_features
+    num_classes = 2
+    # dataset = input_fn("HTRU_2.csv", num_epochs, False, batch_size)
+
+    ins = tf.placeholder("float", [None, num_inputs])
+    outs = tf.placeholder("float", [None, _NUM_CLASSES])
+
+    weights = {
+        'h1': tf.Variable(tf.random_normal([num_inputs, num_hidden_1])),
+        'h2': tf.Variable(tf.random_normal([num_hidden_1, num_hidden_2])),
+        'h3': tf.Variable(tf.random_normal([num_hidden_2, num_hidden_3])),
[…]

### 2018-04-19 ancillary/reclassify.py

@@ -1,0 +1,20 @@
+import os
+
+file = 'HTRU_2.csv'
+ofile = 'HTRU_2_inverse.csv'
+new_data = []
+
+with open(file, 'r') as f:
+    data = f.read()   
+    data = data.split('\n') 
+    for i, item in enumerate(data):
+        if item[-1] == '1':
+            # print(item[-1])
+            new_data.append(item[:len(item)-1] + '0')
+        else:
+            new_data.append(item[:len(item)-1] + '1')
+
+
+with open(ofile, 'w') as w:
+    for item in new_data:
+        w.write(item + "\n")

### 2018-04-19 ancillary/test_csv_to_svg.py

@@ -1,0 +1,19 @@
+import matplotlib.pyplot as plt
+
+fig = plt.figure()
+
+plt.subplot(221) # 2 rows, 2 columns, plot 1
+plt.plot([1,2,3])
+
+plt.subplot(222) # 2 rows, 2 columns, plot 2
+plt.plot([3,1,3])
+
+plt.subplot(223) # 2 rows, 2 columns, plot 3
+plt.plot([3,2,1])
+
+plt.subplot(224) # 2 rows, 2 columns, plot 4
+plt.plot([1,3,1])
+
+plt.show()
+
+fig.savefig('test.svg')

### 2018-04-19 classifier.py

@@ -1,105 +1,0 @@
-
-from __future__ import absolute_import
-from __future__ import division
-from __future__ import print_function
-
-import argparse
-import os
-import shutil
-import sys
-
-import tensorflow as tf 
-import pandas as pd
-from sklearn.datasets import make_classification
-from sklearn.model_selection import train_test_split
-import numpy as np
-
-
-from input_data import input_fn
-_NUM_CLASSES = 2
-
-# https://github.com/soerendip/Tensorflow-binary-classification/blob/master/Tensorflow-binary-classification-model.ipynb
-def simple_model(in_tensor, num_inputs, num_classes, weights, biases):
-    layer_1 = tf.add(tf.matmul(in_tensor, weights['h1']), biases['b1'])
-    layer_1 = tf.nn.relu(layer_1)
-    layer_2 = tf.add(tf.matmul(layer_1, weights['h2']), biases['b2'])
-    layer_2 = tf.nn.relu(layer_2)
-    layer_3 = tf.add(tf.matmul(layer_2, weights['h3']), biases['b3'])
-    layer_3 = tf.nn.relu(layer_3)
-
-    out_tensor = tf.matmul(layer_3, weights['out']) + biases['out']
-    return out_tensor
-
-
-def main(argv):
-    learning_rate = 0.001
-    num_epochs = 100
-    batch_size = 100 
-    num_hidden_1 = 15
-    num_hidden_2 = 15
-    num_hidden_3 = 15
-
-    num_features = 8
-    X, Y = make_classification(n_samples=50000, n_features=num_features, n_informative=8, 
-                           n_redundant=0, n_clusters_per_class=2)
-    Y = np.array([Y, -(Y-1)]).T  # The model currently needs one column for each class
-    X, X_test, Y, Y_test = train_test_split(X, Y)
-
-    num_inputs = num_features
-    num_classes = 2
-    # dataset = input_fn("HTRU_2.csv", num_epochs, False, batch_size)
-
-    ins = tf.placeholder("float", [None, num_inputs])
-    outs = tf.placeholder("float", [None, _NUM_CLASSES])
-
-    weights = {
-        'h1': tf.Variable(tf.random_normal([num_inputs, num_hidden_1])),
-        'h2': tf.Variable(tf.random_normal([num_hidden_1, num_hidden_2])),
-        'h3': tf.Variable(tf.random_normal([num_hidden_2, num_hidden_3])),
[…]

### 2018-04-19 input_data.py

@@ -36,7 +36,7 @@ def train_input_fn(features, labels, batch_size):
     dataset = tf.data.Dataset.from_tensor_slices((dict(features), labels))
 
     # Shuffle, repeat, and batch the examples.
-    dataset = dataset.shuffle(14000).repeat().batch(batch_size)
+    dataset = dataset.shuffle(buffer_size=batch_size, reshuffle_each_iteration=True).repeat().batch(batch_size)
 
     # Return the dataset.
     return dataset

### 2018-04-19 main.py

@@ -3,6 +3,7 @@ from __future__ import division
 from __future__ import print_function
 import tensorflow as tf
 from math import sqrt
+import sys
 
 # from input_data import input_fn, train_input_fn, eval_input_fn
 from csv_class import CSV
@@ -10,12 +11,12 @@ from model import model_Adagrad, model_RMSProp
 from network import run_network
 
 _TEST_PERCENTAGE = 0.2
-_TRAIN = 10 #int(17898*(1-_TEST_PERCENTAGE))
-_BATCH_SIZE = int(_TRAIN*.1)
+_TRAIN = int(17898*(1-_TEST_PERCENTAGE))
+_BATCH_SIZE = max(int(_TRAIN*.01), 1)
 _MODEL = model_RMSProp
 
 # Create a CSV object
-csv = CSV(name='HTRU_2_inverse.csv',
+csv = CSV(name='HTRU_2.csv',
           col_names=['mean_IP', 'std_IP', 'e_kurtosis_IP', 'skewness_IP', 'mean_DM', 'std_DM', 'e_kurtosis_DM', 'skewness_DM', 'class'], 
           label_name='class', 
           col_defaults=[[0.0], [0.0], [0.0], [0.0], [0.0], [0.0], [0.0], [0.0], [0]], 
@@ -23,19 +24,28 @@ csv = CSV(name='HTRU_2_inverse.csv',
                         'test': int(_TRAIN*_TEST_PERCENTAGE)}, 
           classes=2)
 
-
+# Based on CSV file:
 _NODES_PER_LAYER = int((len(csv.col_defaults) - 1) * 1.5)
 _LAYERS = max(int(sqrt(_NODES_PER_LAYER)), 2)
 _HIDDEN_LAYERS = [_NODES_PER_LAYER]*_LAYERS
 
 def main(argv):
-    # print('\nTest set accuracy: {accuracy:0.3f}\n'.format(run_network(csv, _MODEL, _HIDDEN_LAYERS, _BATCH_SIZE, _TEST_PERCENTAGE)))
-    runs = 20
+    runs = 1
+    try:
+        if len(argv) > 1:
+            runs = int(argv[1])        
+    except ValueError:
+        print("Please specify an integer amount of runs or nothing at all")
+        exit()
+    
     total_acc = 0.0
-    for _ in range(runs):
-        total_acc += run_network(csv, _MODEL, _HIDDEN_LAYERS, _BATCH_SIZE, _TEST_PERCENTAGE)['accuracy']
[…]

### 2018-04-19 model.py

@@ -6,9 +6,7 @@ import tensorflow as tf
 
 
 def model_Adagrad(features, labels, mode, params):
-    """DNN with three hidden layers, and dropout of 0.1 probability."""
-    # Create three fully connected layers each layer having a dropout
-    # probability of 0.1.
+    """DNN with params['hidden_units'] hidden layers."""
     net = tf.feature_column.input_layer(features, params['feature_columns'])
     for units in params['hidden_units']:
         net = tf.layers.dense(net, units=units, activation=tf.nn.selu)
@@ -51,15 +49,13 @@ def model_Adagrad(features, labels, mode, params):
 
 
 def model_RMSProp(features, labels, mode, params):
-    """DNN with X hidden layers, and dropout of 0.1 probability."""
-    # Create three fully connected layers each layer having a dropout
-    # probability of 0.1.
+    """DNN with params['hidden_units'] hidden layers."""
     net = tf.feature_column.input_layer(features, params['feature_columns'])    
     for units in params['hidden_units']:
-        net = tf.layers.dense(net, units=units, activation=tf.nn.crelu)
+        net = tf.layers.dense(net, units=units, activation=tf.nn.selu)
 
 
-    # Compute logits (1 per class).
+    # Compute 1 logit per class
     logits = tf.layers.dense(net, params['n_classes'], activation=None)
 
     # Compute predictions.
@@ -80,11 +76,13 @@ def model_RMSProp(features, labels, mode, params):
                                    predictions=predicted_classes,
                                    name='acc_op')
     metrics = {'accuracy': accuracy}
+    # Add accuracy to Tensorboard
     tf.summary.scalar('accuracy', accuracy[1])
 
     if mode == tf.estimator.ModeKeys.EVAL:
-        return tf.estimator.EstimatorSpec(
-            mode, loss=loss, eval_metric_ops=metrics)
+        return tf.estimator.EstimatorSpec(mode, 
+                                          loss=loss, 
+                                          eval_metric_ops=metrics)
 
     # Create training op.
     assert mode == tf.estimator.ModeKeys.TRAIN

### 2018-04-19 network.py

@@ -2,7 +2,7 @@ import tensorflow as tf
 from input_data import input_fn, train_input_fn, eval_input_fn
  
 
-def run_network(csv, model, hidden_layers, batch_size, test_percent):
+def run_network(csv, model, hidden_layers, batch_size, test_percent, run):
     # Read in a CSV object
     (train_x, train_y), (test_x, test_y) = input_fn(data_file=csv.name,
                                                     col_names=csv.col_names,
@@ -15,6 +15,7 @@ def run_network(csv, model, hidden_layers, batch_size, test_percent):
         my_feature_columns.append(tf.feature_column.numeric_column(key=key))
     classifier = tf.estimator.Estimator(
         model_fn=model,
+        model_dir="model_" + str(run),
         params={
             'feature_columns': my_feature_columns,
             'hidden_units': hidden_layers,
@@ -23,8 +24,8 @@ def run_network(csv, model, hidden_layers, batch_size, test_percent):
         })
 
     # Train the Model.
-    with tf.device('/device:GPU:0'):
-    # with tf.device('/cpu:0'):
+    # with tf.device('/device:GPU:0'):
+    with tf.device('/cpu:0'):
         classifier.train(
             input_fn=lambda:train_input_fn(train_x, train_y, batch_size),
             steps=csv.num_examples['train'])

### 2018-04-19 ancillary/plot_2D_csv.py
Added ancillary scripts and test images. Also converted Accuracy and loss to svg. The loss instantly drops during training because it trains so fast...graph looks weird.

@@ -1,0 +1,72 @@
+# https://pythonprogramming.net/loading-file-data-matplotlib-tutorial/
+
+# Base implementation, works
+# import matplotlib.pyplot as plt
+# import csv
+
+# fig = plt.figure()
+
+# X = []
+# Y = []
+
+# with open('HTRU_2_inverse.csv','r') as csvfile:
+#     plots = csv.reader(csvfile, delimiter=',')
+#     for row in plots:
+#         X.append(float(row[1]))
+#         Y.append(float(row[2]))
+
+# plt.plot(X,Y, label='Loaded from file!')
+# plt.xlabel('X')
+# plt.ylabel('Y')
+# plt.title('Interesting Graph\nCheck it out')
+# plt.legend()
+# plt.show()
+# fig.savefig('test_2D.svg')
+
+
+import matplotlib.pyplot as plt
+import csv
+import sys
+
+def main():
+    """This is intended to take CSV files with headers and turn them into SVG files. These 
+       files are intended to be from Tensorboard."""
+
+    if len(sys.argv) != 3:
+        print("Please specify input and output files as arguments: \"input.csv output\"")
+        exit()
+
+    i_file = sys.argv[1]
+    o_file = sys.argv[2]
+
+    if not sys.argv[1].endswith('.csv'):
+        i_file = i_file + '.csv'
+
+    if not sys.argv[2].endswith('.svg'):
+        o_file = o_file + '.svg'
+    
+    fig = plt.figure()
+
+    X = []
+    Y = []
+
+    with open(i_file,'r') as csvfile:
+        plots = csv.reader(csvfile, delimiter=',')
+        next(plots, None) # skip headers
+        for row in plots:
+            # row[0] is wall time, don't care about it
+            X.append(float(row[1]))
+            Y.append(float(row[2]))
+
+    plt.subplot(111, adjustable='box', aspect='auto')
+    plt.plot(X,Y, label='Loss')
+    plt.xlabel('X')
+    plt.ylabel('Y')
+    plt.title(i_file[:-4] + ' over steps')
+    plt.legend(loc=0) # 0: top right .... 4: bottom right
+
+    plt.show()
+    fig.savefig(o_file)
+
+if __name__ == '__main__':
+    main()

### 2018-04-19 ancillary/plot_3D_csv.py

@@ -1,0 +1,27 @@
+from mpl_toolkits.mplot3d import axes3d
+import matplotlib.pyplot as plt
+import csv
+
+fig = plt.figure()
+ax = fig.add_subplot(111, projection='3d')
+
+# Grab some test data.
+X = []
+Y = []
+Z = []
+
+with open('HTRU_2_inverse.csv','r') as csvfile:
+    plots = csv.reader(csvfile, delimiter=',')
+    for row in plots:
+        X.append(float(row[2]))
+        Y.append(float(row[3]))
+        Z.append(float(row[4]))
+
+# Plot a basic wireframe.
+# ax.plot_wireframe(X, Y, Z, rstride=20, cstride=30)
+
+# Plot a basic scatter plot.
+ax.scatter(X, Y, Z)
+
+plt.show()
+fig.savefig('test_3D_scatter.svg')

### 2018-04-19 ancillary/plot_2D_csv.py
Made plot_2D_csv able to run without calling main.

@@ -1,50 +1,21 @@
+# Assistance via:
 # https://pythonprogramming.net/loading-file-data-matplotlib-tutorial/
-
-# Base implementation, works
-# import matplotlib.pyplot as plt
-# import csv
-
-# fig = plt.figure()
-
-# X = []
-# Y = []
-
-# with open('HTRU_2_inverse.csv','r') as csvfile:
-#     plots = csv.reader(csvfile, delimiter=',')
-#     for row in plots:
-#         X.append(float(row[1]))
-#         Y.append(float(row[2]))
-
-# plt.plot(X,Y, label='Loaded from file!')
-# plt.xlabel('X')
-# plt.ylabel('Y')
-# plt.title('Interesting Graph\nCheck it out')
-# plt.legend()
-# plt.show()
-# fig.savefig('test_2D.svg')
-
 
 import matplotlib.pyplot as plt
 import csv
 import sys
 
-def main():
+def run_conversion(i_file, o_file):
     """This is intended to take CSV files with headers and turn them into SVG files. These 
-       files are intended to be from Tensorboard."""
+           files are intended to be from Tensorboard."""
 
-    if len(sys.argv) != 3:
-        print("Please specify input and output files as arguments: \"input.csv output\"")
-        exit()
-
-    i_file = sys.argv[1]
-    o_file = sys.argv[2]
-
-    if not sys.argv[1].endswith('.csv'):
+    # Handle extensions
+    if not i_file.endswith('.csv'):
         i_file = i_file + '.csv'
 
-    if not sys.argv[2].endswith('.svg'):
+    if not o_file.endswith('.svg'):
         o_file = o_file + '.svg'
-    
+        
     fig = plt.figure()
 
     X = []
@@ -59,14 +30,27 @@ def main():
             Y.append(float(row[2]))
 
     plt.subplot(111, adjustable='box', aspect='auto')
-    plt.plot(X,Y, label='Loss')
-    plt.xlabel('X')
-    plt.ylabel('Y')
+    plt.plot(X,Y, label='Loss/Advantage')
+    plt.xlabel('Step')
+    plt.ylabel('Advantage')
     plt.title(i_file[:-4] + ' over steps')
     plt.legend(loc=0) # 0: top right .... 4: bottom right
 
     plt.show()
     fig.savefig(o_file)
+
+
+def main():
+    if len(sys.argv) != 3:
[…]

### 2018-04-19 ancillary/plot_2D_csv.py
Fixed axis labels on plots.

@@ -30,9 +30,9 @@ def run_conversion(i_file, o_file):
             Y.append(float(row[2]))
 
     plt.subplot(111, adjustable='box', aspect='auto')
-    plt.plot(X,Y, label='Loss/Advantage')
-    plt.xlabel('Step')
-    plt.ylabel('Advantage')
+    plt.plot(X,Y, label='Loss/Steps')
+    plt.xlabel('Steps')
+    plt.ylabel('Loss')
     plt.title(i_file[:-4] + ' over steps')
     plt.legend(loc=0) # 0: top right .... 4: bottom right
 

### 2018-04-22 paper/paper.tex
Started assembling the paper. The classification was done a while ago but this was delayed due to senior design.

@@
 \usepackage{microtype}      % microtypography
+\usepackage{amsmath}
+\usepackage{algorithm}
+\usepackage{algorithmic}
 
-\title{Formatting instructions for NIPS 2017}
-
-% The \author macro works with any number of authors. There are two
-% commands used to separate the names and addresses of multiple
-% authors: \And and \AND.
-%
-% Using \And between authors leaves it to LaTeX to determine where to
-% break the lines. Using \AND forces a line break at that point. So,
-% if LaTeX puts 3 of 4 authors names on the first line, and the last
-% on the second line, try using \AND instead of \And before the third
-% author name.
+\title{Pulsar Classification using Deep Neural Networks}
 
 \author{
-  Kyle W.~MacMillan\thanks{Use footnote for providing further
-    information about author (webpage, alternative
-    address)---\emph{not} for acknowledging funding agencies.} \\
+  Kyle W.~MacMillan
   Department of Computer Science\\
-  Cranberry-Lemon University\\
-  Pittsburgh, PA 15213 \\
-  \texttt{hippo@cs.cranberry-lemon.edu} \\
-  %% examples of more authors
-  %% \And
-  %% Coauthor \\
-  %% Affiliation \\
-  %% Address \\
-  %% \texttt{email} \\
-  %% \AND
-  %% Coauthor \\
-  %% Affiliation \\
-  %% Address \\
-  %% \texttt{email} \\
-  %% \And
-  %% Coauthor \\
-  %% Affiliation \\
-  %% Address \\
-  %% \texttt{email} \\
-  %% \And
-  %% Coauthor \\
-  %% Affiliation \\
-  %% Address \\
-  %% \texttt{email} \\
+  South Dakota School of Mines and Technology\\
+  Rapid City, SD 57701 \\
+  \texttt{kyle.macmillan@mines.sdsmt.edu} \\
 }
@@
 \begin{document}
-% \nipsfinalcopy is no longer used
 
@@
 \begin{abstract}
-  The abstract paragraph should be indented \nicefrac{1}{2}~inch
-  (3~picas) on both the left- and right-hand margins. Use 10~point
-  type, with a vertical spacing (leading) of 11~points.  The word
-  \textbf{Abstract} must be centered, bold, and in point size 12. Two
-  line spaces precede the abstract. The abstract must be limited to
-  one paragraph.
+  Pulsars are rapidly rotating, highly magnetized, neutron stars and white 
+  dwarfs that emit focused electromagnetic radiation in a beam. The beam is 
+  only visible to us when it is directly facing Earth and is the reason for 
+  their pulsed nature. This paper approaches classification of pulsars and 
+  non-pulsars with the intent of learning more about TensorFlow. The 
+  classification method used is Deep Neural Networks and an acceptable level of 
+  accuracy was obtained.
 \end{abstract}
 
-\section{Submission of papers to NIPS 2017}
+\section{Introduction}
+  We were tasked with picking a dataset and training a deep learning network. 
+  First thing to do was to pick a dataset. Being an open-ended assignment there 
+  was uncertainty as to what particular dataset to explore. Initial looks 
+  involved different image classification datasets such as CIFAR-10, 
+  Caltech 101, and NORB. Down the road there is no desire to work with image 
+  data classification, work with files and datasets of continuous and 
+  discrete data are preferred. After thorough search of the available datasets 
+  it was decided pulsar classification best suited this paper.
 
-NIPS requires electronic submissions.  The electronic submission site
-is
-\begin{center}
-  \url{https://cmt.research.microsoft.com/NIPS2017/}
-\end{center}
+  The last decision before pressing on to data format was to pick the correct 
+  deep learning framework for the job. There were several options but TensorFlow 
+  seemed like a good choice. Keras and PyTorch are other tools that utilize 
+  TensorFlow but were not used because those are often considered a "front end" 
+  for TensorFlow, which was not part of the goals of the assignment.
 
-Please read carefully the instructions below and follow them
-faithfully.
+\section{Method}
 
-\subsection{Style}
+\subsection{Data Format}
+  After determining the dataset and the framework to be utilized it is 
+  necessary to figure out how to read data from the dataset. A modular approach 
+  was taken with this project. Users will be able to select a comma-separated 
+  values (CSV) file to load in. By specifying a class to contain the CSV data it 
+  is possible to run multiple datasets while making only minor modifications to 
+  the code. The format is also much easier to read as a result of the class 
+  format.
 
-Papers to be submitted to NIPS 2017 must be prepared according to the
-instructions presented here. Papers may only be up to eight pages
-long, including figures. This does not include acknowledgments and 
-cited references which are allowed on subsequent pages.
-Papers that exceed these limits will not be reviewed, or in any
-other way considered for presentation at the conference.
+  Rather than code up a custom method of moving CSV data into a format usable by 
+  the deep learning framework it was determined to "stand on the shoulders of 
+  giants". Pandas was used to bring CSV data into usable form. After pulling the 
+  data into a single structure it was necessary to split the data into training 
+  and testing data. Again, rather than code that from scratch it was determined 
+  best practice to utilize existing tools.
 
-The margins in 2017 are the same as since 2007, which allow for
-$\sim$$15\%$ more words in the paper compared to earlier years.
+  For that endevour scikit-learn was used, specifically the 
+  $train\_test\_split()$ method. As is standard for classification problems the 
+  data was segmented into 80\% training and 20\% testing data. It was then 
+  necessary to place the $class$ label into a data structure for later. For both 
+  the train and test data, associated labels are passed, along with the data, 
+  as tuples. The psuedocode for this section can be found under Algorithm 
+  \ref{alg:input_fn}.
 
-Authors are required to use the NIPS \LaTeX{} style files obtainable
-at the NIPS website as indicated below. Please make sure you use the
-current files and not previous versions. Tweaking the style files may
-be grounds for rejection.
+  \begin{algorithm}
+    \caption{$input\_fn()$}
+    \label{alg:input_fn}
+    \begin{algorithmic}
+      \STATE $data \gets CSV$\\
+      \STATE $test, train \gets train\_test\_split(data)$
+      \STATE $test\_label \gets test.pop(class)$
+      \STATE $train\_label \gets train.pop(class)$
+      \RETURN $(train, train\_label), (test,test\_label)$
+    \end{algorithmic}
+  \end{algorithm}
 
-\subsection{Retrieval of style files}
+\section{Retrieval of style files}
 

### 2018-04-22 main.py

@@ -12,7 +12,7 @@ from network import run_network
 
 _TEST_PERCENTAGE = 0.2
 _TRAIN = int(17898*(1-_TEST_PERCENTAGE))
-_BATCH_SIZE = max(int(_TRAIN*.01), 1)
+_BATCH_SIZE = max(int(_TRAIN*.1), 1)
 _MODEL = model_RMSProp
 
 # Create a CSV object
@@ -44,8 +44,8 @@ def main(argv):
         print("Run: ", run)
         total_acc += run_network(csv, _MODEL, _HIDDEN_LAYERS, _BATCH_SIZE, _TEST_PERCENTAGE, run)['accuracy']
 
-
-    print("Accuracy = ", total_acc / runs)
+    csv.accuracy = total_acc / runs
+    print("Accuracy = ", csv.accuracy)
 
 if __name__ == '__main__':
     tf.logging.set_verbosity(tf.logging.INFO)

### 2018-04-22 network.py

@@ -4,14 +4,14 @@ from input_data import input_fn, train_input_fn, eval_input_fn
 
 def run_network(csv, model, hidden_layers, batch_size, test_percent, run):
     # Read in a CSV object
-    (train_x, train_y), (test_x, test_y) = input_fn(data_file=csv.name,
-                                                    col_names=csv.col_names,
-                                                    test_percentage=test_percent,
-                                                    label_name=csv.label_name)
+    (train_feat, train_label), (test_feat, test_label) = input_fn(data_file=csv.name,
+                                                                  col_names=csv.col_names,
+                                                                  test_percentage=test_percent,
+                                                                  label_name=csv.label_name)
 
     # Feature columns describe how to use the input.
     my_feature_columns = []
-    for key in train_x.keys():
+    for key in train_feat.keys():
         my_feature_columns.append(tf.feature_column.numeric_column(key=key))
     classifier = tf.estimator.Estimator(
         model_fn=model,
@@ -27,11 +27,11 @@ def run_network(csv, model, hidden_layers, batch_size, test_percent, run):
     # with tf.device('/device:GPU:0'):
     with tf.device('/cpu:0'):
         classifier.train(
-            input_fn=lambda:train_input_fn(train_x, train_y, batch_size),
+            input_fn=lambda:train_input_fn(train_feat, train_label, batch_size),
             steps=csv.num_examples['train'])
 
     # Evaluate the model.
     eval_result = classifier.evaluate(
-        input_fn=lambda:eval_input_fn(test_x, test_y, batch_size))
+        input_fn=lambda:eval_input_fn(test_feat, test_label, batch_size))
     
     return eval_result

### 2018-04-23 paper/paper.tex
Mostly done with the paper. Finalizing, spellchecking, adding any other citations.

@@
 \usepackage{microtype}      % microtypography
+\usepackage{pdfpages}       % Because LaTeX doesn't take SVGs...
 \usepackage{amsmath}
@@
 \usepackage{algorithmic}
+\usepackage{natbib}
 
@@
   The last decision before pressing on to data format was to pick the correct 
-  deep learning framework for the job. There were several options but TensorFlow 
-  seemed like a good choice. Keras and PyTorch are other tools that utilize 
-  TensorFlow but were not used because those are often considered a "front end" 
-  for TensorFlow, which was not part of the goals of the assignment.
+  deep learning framework for the job. There were several options but 
+  TensorFlow seemed like a good choice. Keras and PyTorch are other tools that 
+  utilize TensorFlow but were not used because those are often considered a 
+  "front end" for TensorFlow, which was not part of the goals of the 
+  assignment.
 
@@
 
-\subsection{Data Format}
+\subsection{Main}
+  Main.py is where the project is ran from. There are several hyperparameters 
+  that a user can pick, beginning with $\_TEST\_PERCENTAGE$, which sets the 
+  percentage of comma-separated values (CSV) data to be utilized for testing. 
+  Industry standard is 20\%, so that is the default setting. The training data 
+  $\_TRAIN$ is, as a result, 80\% of the CSV data. 
+  % 
+  \[\mathcal{\_TRAIN}=\_NUM\_ELEMENTS * ( 1 - \_TEST\_PERCENTAGE )\]
+  % 
+  It was necessary to hard-code in the number of elements in the CSV file because there was trouble when trying to run update on the CSV class due to 
+  an incomplete understanding of python abilities such as $class.update()$.
+
+  $\_BATCH\_SIZE$ is set as 
+  %
+  \[\mathcal{\_BATCH\_SIZE}=max\{\_TRAIN*0.1, 1\}\]
+  %
+  This is part of ensuring the training does not get stuck in local minima. \_MODEL is then set as whichever optimizer the user would like, in this case, 
+  RMSPropOptimizer was selected. A CSV class is created based on the dataset to 
+  be classified.
+
+  Hyperparameter choices are part of the art of machine learning but in this 
+  project it was not the focus to make perfect hyperparameters. That being 
+  said, that was explored briefly for this project as seen in section 
+  \ref{sec:hyperparams}. $\_NODES\_PER\_LAYER$ was one of such hyperparameters, 
+  as was $\_LAYERS$, and $\_HIDDEN\_LAYERS$. The final implementation of these 
+  parameters are as follows:
+  %
+  \[\mathcal{\_NODES\_PER\_LAYER}=(num\_features - 1) * 1.5\]
+  \[\mathcal{\_LAYERS}=max\{sqrt(\_NODES\_PER\_LAYER), 2\}\]
+  \[\mathcal{\_HIDDEN\_LAYERS}=[\_NODES\_PER\_LAYER] * \_LAYERS\]
+  %
+  This lead to 3 hidden layers with 12 nodes each for the \href{https://archive.ics.uci.edu/ml/datasets/HTRU2}{HTRU\_2 Dataset}.
+
+  After all parameters have been setup main gets run. Users can select the 
+  number of runs to perform as an argument when they begin the program e.g. 
+  %
+  \[\textnormal{python\ main.py \textit{X}}\]  
+  %
+  The program will then run the classifier \textit{X} times. After finishing 
+  the program will output classification accuracy of the given dataset.
+
+\subsection{Data format}
   After determining the dataset and the framework to be utilized it is 
   necessary to figure out how to read data from the dataset. A modular approach 
-  was taken with this project. Users will be able to select a comma-separated 
-  values (CSV) file to load in. By specifying a class to contain the CSV data it 
-  is possible to run multiple datasets while making only minor modifications to 
-  the code. The format is also much easier to read as a result of the class 
-  format.
+  was taken with this project. Users will be able to select a CSV file to load 
+  in. By specifying a class to contain the CSV data it is possible to run 
+  multiple datasets while making only minor modifications to the code. The 
+  format is also much easier to read as a result of the class format.
 
-  Rather than code up a custom method of moving CSV data into a format usable by 
-  the deep learning framework it was determined to "stand on the shoulders of 
-  giants". Pandas was used to bring CSV data into usable form. After pulling the 
-  data into a single structure it was necessary to split the data into training 
-  and testing data. Again, rather than code that from scratch it was determined 
-  best practice to utilize existing tools.
+  Rather than code up a custom method of moving CSV data into a format usable 
+  by the deep learning framework it was determined to "stand on the shoulders 
+  of giants". Pandas was used to bring CSV data into usable form. After pulling 
+  the data into a single structure it was necessary to split the data into 
+  training and testing data. Again, rather than code that from scratch it was 
+  determined best practice to utilize existing tools.
 
@@
   data was segmented into 80\% training and 20\% testing data. It was then 
-  necessary to place the $class$ label into a data structure for later. For both 
-  the train and test data, associated labels are passed, along with the data, 
-  as tuples. The psuedocode for this section can be found under Algorithm 
+  necessary to place the $class$ label into a data structure for later. For 
+  both the train and test data, associated labels are passed, along with the 
+  data, as tuples. The psuedocode for this section can be found under Algorithm 
   \ref{alg:input_fn}.
-
+  %
   \begin{algorithm}
@@
   \end{algorithm}
+  %
+\subsection{TensorFlow estimator}
+  TensorFlow has built in estimators such as:
+  %
+  \begin{itemize}
+    \item \href{https://www.tensorflow.org/api_docs/python/tf/estimator/DNNClassifier}{DNNClassifier}
+    \item \href{https://www.tensorflow.org/api_docs/python/tf/estimator/BaselineClassifier}{BaselineClassifier}
+    \item \href{https://www.tensorflow.org/api_docs/python/tf/estimator/BaselineRegressor}{BaselineRegressor}
+    \item \href{https://www.tensorflow.org/api_docs/python/tf/estimator/DNNLinearCombinedClassifier}{DNNLinearCombinedClassifier}
+    \item \href{https://www.tensorflow.org/api_docs/python/tf/estimator/LinearClassifier}{LinearClassifier}
+    \item \href{https://www.tensorflow.org/api_docs/python/tf/estimator/LinearRegressor}{LinearRegressor}
+  \end{itemize}
+  %
+  You also have the ability to build your own estimator, or classifier, and 
+  this is the route that was selected for this project. The custom estimator 
+  selected utilizes the $model$ specified at the start of the program, a 
+  $model\_dir$ for TensorBoard output which will be discussed in section 
+  \ref{sec:tensorboard}, and the $params$ which consist of $feature\_columns$, 
+  $hidden\_units$, and $n\_classes$.
 
-\section{Retrieval of style files}
+  Estimator also requires \href{https://www.tensorflow.org/versions/r1.2/api_docs/python/tf/estimator/ModeKeys}{three modes} depending on the goal:
+  %
+  \begin{itemize}
+    \item ModeKeys.TRAIN
+    \item ModeKeys.EVAL
+    \item ModeKeys.PREDICT
+  \end{itemize}
+  %
+  Lastly, the estimator requires a return of $EstimatorSpec$. Documentation for 
+  the EstimatorSpec can be found on \href{https://www.tensorflow.org/api_docs/python/tf/estimator/EstimatorSpec}{TensorFlow's website}.
+It is important to note that each of the different $ModeKeys$ requires a different set of parameters for the returned $EstimatorSpec$.
 
-The style files for NIPS and other conference information are
-available on the World Wide Web at
+\subsection{Training}
+  TensorFlow offers the ability to train estimators by calling a $train()$ 
+  method. For this paper the $input\_fn$ and $steps$ arguments are set by a 
+  function call to $train\_input\_fn$ and $csv.num\_examples['train']$ 
+  respectively. This allows the data to be segmented for training.
+
+  The model that was instantiated during estimator creation is detailed under
+  $\textnormal{model.model\_RMSProp}$. For each of the layers that was passed 
+  to it under $params['hidden\_units']$ there is a fully connected layer built 
+  with selu activation. \citet{selu} found with the proper math you can obtain 
+  self-normalizing exponential linear units, meaning they don't require batch 
+  normalization and that is why they were chosen over all of the other 
+  activation functions. There is also the final fully connected layer which has 
+  no activation layer. This final layer aids in determining the classification.
+
+  During training ModeKeys.TRAIN is called, which specifies RMSProp gradient 
+  descent as our optimizer and then calls $minimize()$. The $minimize()$ method 
+  will automatically compute the gradients and apply them to the variables, but 
+  if you need to tune the network there are additional steps that can be taken 
+  instead:
+  %
+  \begin{enumerate}
+    \item Compute the gradients with $compute\_gradients()$
+    \item Process the gradients as you wish
+    \item Apply the processed gradients with $apply\_gradients()$
+  \end{enumerate}
+  %
+  Further documentation on this process can be found on TensorFlow's website 
+  under the \href{https://www.tensorflow.org/api_docs/python/tf/train/Optimizer}
+  {class Optimizer}. It was not necessary to have that level of fidelity with 
+  this particular dataset, so the base $minimize()$ was all that was necessary.
+
+  With $minimize()$ minimizing the loss we are able to make progress towards a 
+  classification. This dataset in particular minimizes loss to near-zero after 
+  just the first episode of 100 training steps as can be seen in Figure \ref{img:loss}.
+
+\subsection{Hyperparameters}\label{sec:hyperparams}
+  Hyperparameters are normally very important but in this dataset it was 
+  discovered that they had very little impact on the efficacy of 
+  this classifier.
+
+  An example of hyperparameter randomization can be found under:
+  %
+  \[\textnormal{python\ hyperparams.py}\]
+  %
+  That file will automatically generate randomized hyperparameters. During 
+  testing of this project various hyperparameters were tested with no 
+  significant improvements over the initial parameters set so the associated 
+  code was removed from primary operation of the classifier. The file described 
+  would allow for random testing of hyperparameters across any number of 
+  computers. \citet{hypparam} found random search of hyperparameters to be superior to grid search and was the method used while exploring 
+  hyperparameter tuning during this project.
+
+\subsection{TensorBoard}\label{sec:tensorboard}
+  One of the other reasons for utilizing TensorFlow is the TensorBoard project. 
+  TensorBoard allows for visualization of various parameters as defined by the 
+  user. Figure \ref{img:acc_smooth} and \ref{img:loss_smooth} are the same results as shown in Figure \ref{img:accuracy} and \ref{img:loss} 
+  respectively. The smooothing helps in understanding what may be going on, 
+  especially in more turbulant graphs. Another benefit is being able to 
+  visualize the graph structure. To use TensorBoard on this project ensure it 
+  was installed with TensorFlow and type 
+  \[\textnormal{tensorboard\ -\--logdir\ model}\]
+  and go to the link it provides (by ctrl clicking or copy/paste).
+
+  \begin{figure}[H]
+  \caption{Smoothed Accuracy}\label{img:acc_smooth}
   \begin{center}
-  \url{http://www.nips.cc/}
+  \includegraphics[scale=0.65]{../images/acc}
   \end{center}
-The file \verb+nips_2017.pdf+ contains these instructions and
-illustrates the various formatting requirements your NIPS paper must
-satisfy.
+  \end{figure}
+  %
+  \begin{figure}[H]
+  \caption{Smoothed Loss}\label{img:loss_smooth}
+  \begin{center}
+  \includegraphics[scale=0.65]{../images/loss}
+  \end{center}
+  \end{figure}
 
-The only supported style file for NIPS 2017 is \verb+nips_2017.sty+,
-rewritten for \LaTeXe{}.  \textbf{Previous style files for \LaTeX{}
-  2.09, Microsoft Word, and RTF are no longer supported!}
+\newpage
+\section{Results}\label{sec:results}
+  RMSProp gradient descent with 0.001 learning rate, performing batch runs on 
+  10\% of the training samples every 100 steps produced an accuracy of 97.8\% 
+  averaged over 20 tests. These were taken with 80\% train and 20\% test 
+  samples. Other hyperparameters were three fully connected layers with 12 
+  nodes each using selu activation.
 
-The new \LaTeX{} style file contains two optional arguments:
-\verb+final+, which creates a camera-ready copy, and \verb+nonatbib+,
-which will not load the \verb+natbib+ package for you in case of
-package clash.
+  \begin{figure}[H]
+  \caption{Accuracy}\label{img:term_acc}
+  \begin{center}
+  \includegraphics[scale=0.75]{../images/accuracy_percent_small}
+  \end{center}
+  \end{figure}
+  %
+  \begin{figure}[H]
+  \caption{Accuracy}\label{img:accuracy}
+  \begin{center}
+  \includegraphics[scale=0.75]{../images/Accuracy}
+  \end{center}
+  \end{figure}
+  %
+  \begin{figure}[H]
+  \caption{Loss}\label{img:loss}
+  \begin{center}
+  \includegraphics[scale=0.75]{../images/Loss}
+  \end{center}
+  \end{figure}
 
-At submission time, please omit the \verb+final+ option. This will
-anonymize your submission and add line numbers to aid review.  Please
-do \emph{not} refer to these line numbers in your paper as they will
-be removed during generation of camera-ready copies.
-
-The file \verb+nips_2017.tex+ may be used as a ``shell'' for writing
-your paper. All you have to do is replace the author, title, abstract,
-and text of the paper with your own.
-
-The formatting instructions contained in these style files are
-summarized in Sections \ref{gen_inst}, \ref{headings}, and
-\ref{others} below.
+\section{Conclusion}
 
@@
 
+% [4] Bergstra, J.\ \& Bengio, J.\ (2012) Random Search for Hyper-Parameter 
+% Optimization. {\it Journal of Machine Learning Research 13} pp.\ 281-305.
+
+\bibliographystyle{plainnat}
+\bibliography{bib}
 \end{document}

### 2018-04-23 hyperparams.py

@@ -1,0 +1,90 @@
+import random
+import sys
+from numpy import random as np
+
+class HyperParams: 
+    def __init__(self, seed=None):
+        """Fills all self variables in self.params. Sets seed member so it can be appended to workerData folder"""        
+        random.seed(seed)        
+        self.params = { 'learning_rate_min'     : 0.01,
+                        'learning_rate_max'     : 0.1,
+                        'h_nodes_layer_min'     : 12,
+                        'h_nodes_layer_max'     : 36,
+                        'base_explr_min'        : 0.30,
+                        'base_explr_max'        : 0.99,
+                        'rand_explr_A_min'      : 1.0,
+                        'rand_explr_A_max'      : 4.0,
+                        'rand_explr_B_min'      : 4.0,
+                        'rand_explr_B_max'      : 10.0,
+                        'acc_coef_min'          : 1.0,
+                        'acc_coef_max'          : 1.0,
+                        'advantage_coef_min'    : 2.0,
+                        'advantage_coef_max'    : 8.0,
+                        'max_grad_norm_min'     : 1.0,
+                        'max_grad_norm_max'     : 4.0,
+                        'discount_min'          : 0.93,
+                        'discount_max'          : 1.0,
+                        'consistency_coef_min'  : 0.3,
+                        'consistency_coef_max'  : 0.6
+                      }
+
+        # Set hyperparams
+        self.learning_rate = self.params['learning_rate_max']*self.get_betavariate_value(1, 7) + self.params['learning_rate_min']
+        self.hidden_nodes = int(self.get_uniform_value(self.params['h_nodes_layer_min'], self.params['h_nodes_layer_max']))
+        if self.hidden_nodes % 2 == 0:
+            self.hidden_nodes += 1
+        self.base_xplr_rate = self.get_uniform_value(self.params['base_explr_min'], self.params['base_explr_max'])
+        self.alpha = 1.25
+        self.beta = 5.625
+        self.accuracy_coef = self.get_uniform_value(self.params['acc_coef_min'], self.params['acc_coef_max'])
+        self.advantage_coef = self.get_uniform_value(self.params['advantage_coef_min'], self.params['advantage_coef_max'])
+        self.max_grad_norm = self.get_uniform_value(self.params['max_grad_norm_min'], self.params['max_grad_norm_max'])
+        self.discount = self.get_uniform_value(self.params['discount_min'], self.params['discount_max'])
[…]

### 2018-04-23 main.py

@@ -4,15 +4,18 @@ from __future__ import print_function
 import tensorflow as tf
 from math import sqrt
 import sys
+import shutil # Remove model folder
+import glob
 
 # from input_data import input_fn, train_input_fn, eval_input_fn
 from csv_class import CSV
 from model import model_Adagrad, model_RMSProp
 from network import run_network
 
+_NUM_ELEMENTS = 17898
 _TEST_PERCENTAGE = 0.2
-_TRAIN = int(17898*(1-_TEST_PERCENTAGE))
-_BATCH_SIZE = max(int(_TRAIN*.1), 1)
+_TRAIN = int(_NUM_ELEMENTS*(1-_TEST_PERCENTAGE))
+_BATCH_SIZE = max(int(_TRAIN*.001), 1)
 _MODEL = model_RMSProp
 
 # Create a CSV object
@@ -30,6 +33,10 @@ _LAYERS = max(int(sqrt(_NODES_PER_LAYER)), 2)
 _HIDDEN_LAYERS = [_NODES_PER_LAYER]*_LAYERS
 
 def main(argv):
+    # Clears all previous models
+    for name in glob.glob('model_*'):
+      shutil.rmtree(name)
+    
     runs = 1
     try:
         if len(argv) > 1:
@@ -38,13 +45,12 @@ def main(argv):
         print("Please specify an integer amount of runs or nothing at all")
         exit()
     
-    total_acc = 0.0
     # Allows for multiple runs to acquire an average
     for run in range(runs):
         print("Run: ", run)
-        total_acc += run_network(csv, _MODEL, _HIDDEN_LAYERS, _BATCH_SIZE, _TEST_PERCENTAGE, run)['accuracy']
+        csv.accuracy += run_network(csv, _MODEL, _HIDDEN_LAYERS, _BATCH_SIZE, _TEST_PERCENTAGE, run)['accuracy']
 
-    csv.accuracy = total_acc / runs
+    csv.accuracy = csv.accuracy  / runs
     print("Accuracy = ", csv.accuracy)
 
 if __name__ == '__main__':

### 2018-04-23 paper/paper.tex
Moved images folder to the appropriate location. SVGs were made but ran into trouble importing them so they were converted to PDF. Added reference to dataset paper and added their classification accuracy compared to mine.

@@
 
-% Copy/pasta of nips_2017 for future modification found here:
-% https://nips.cc/Conferences/2017/PaperInformation/StyleFiles
-
-% if you need to pass options to natbib, use, e.g.:
-% \PassOptionsToPackage{numbers, compress}{natbib}
-% before loading nips_2017
-%
-% to avoid loading the natbib package, add option nonatbib:
-% \usepackage[nonatbib]{nips_2017}
-
-\usepackage{nips_2017}
-
-% to compile a camera-ready version, add the [final] option, e.g.:
-% \usepackage[final]{nips_2017}
-
+\usepackage[final]{nips_2017}
 \usepackage[utf8]{inputenc} % allow utf-8 input
@@
     non-pulsars with the intent of learning more about TensorFlow. The 
-  classification method used is Deep Neural Networks and an acceptable level of 
-  accuracy was obtained.
+    classification method used is Deep Neural Networks and an acceptable level 
+    of accuracy was obtained.
 \end{abstract}
@@
     We were tasked with picking a dataset and training a deep learning network. 
-  First thing to do was to pick a dataset. Being an open-ended assignment there 
-  was uncertainty as to what particular dataset to explore. Initial looks 
-  involved different image classification datasets such as CIFAR-10, 
+    First thing to do was to pick a dataset. Being an open-ended assignment 
+    there was uncertainty as to what particular dataset to explore. Initial 
+    looks involved different image classification datasets such as CIFAR-10, 
     Caltech 101, and NORB. Down the road there is no desire to work with image 
     data classification, work with files and datasets of continuous and 
-  discrete data are preferred. After thorough search of the available datasets 
-  it was decided pulsar classification best suited this paper.
+    discrete data are preferred. After thorough search of the available 
+    datasets it was decided pulsar classification provided by 
+    \citet{orig_pulsar} was best suited this paper.
 
@@
     deep learning framework for the job. There were several options but 
-  TensorFlow seemed like a good choice. Keras and PyTorch are other tools that 
-  utilize TensorFlow but were not used because those are often considered a 
-  "front end" for TensorFlow, which was not part of the goals of the 
-  assignment.
+    TensorFlow seemed like a good choice. Keras and PyTorch are other tools 
+    that utilize TensorFlow but were not used because those are often 
+    considered a "front end" for TensorFlow, which was not part of the goals of 
+    the assignment.
 
@@
     percentage of comma-separated values (CSV) data to be utilized for testing. 
-  Industry standard is 20\%, so that is the default setting. The training data 
-  $\_TRAIN$ is, as a result, 80\% of the CSV data. 
+    Industry standard is 20\%, so that is the default setting. The training 
+    data $\_TRAIN$ is, as a result, 80\% of the CSV data. 
     % 
@@
     % 
-  It was necessary to hard-code in the number of elements in the CSV file because there was trouble when trying to run update on the CSV class due to 
+    It was necessary to hard-code in the number of elements in the CSV file 
+    because there was trouble when trying to run update on the CSV class due to 
     an incomplete understanding of python abilities such as $class.update()$.
@@
     %
-  This is part of ensuring the training does not get stuck in local minima. \_MODEL is then set as whichever optimizer the user would like, in this case, 
-  RMSPropOptimizer was selected. A CSV class is created based on the dataset to 
-  be classified.
+    This is part of ensuring the training does not get stuck in local minima. 
+    \_MODEL is then set as whichever optimizer the user would like, in this 
+    case, RMSPropOptimizer was selected. A CSV class is created based on the 
+    dataset to be classified.
 
@@
     said, that was explored briefly for this project as seen in section 
-  \ref{sec:hyperparams}. $\_NODES\_PER\_LAYER$ was one of such hyperparameters, 
-  as was $\_LAYERS$, and $\_HIDDEN\_LAYERS$. The final implementation of these 
-  parameters are as follows:
+    \ref{sec:hyperparams}. $\_NODES\_PER\_LAYER$ was one of such 
+    hyperparameters, as was $\_LAYERS$, and $\_HIDDEN\_LAYERS$. The final 
+    implementation of these parameters are as follows:
     %
@@
     After determining the dataset and the framework to be utilized it is 
-  necessary to figure out how to read data from the dataset. A modular approach 
-  was taken with this project. Users will be able to select a CSV file to load 
-  in. By specifying a class to contain the CSV data it is possible to run 
-  multiple datasets while making only minor modifications to the code. The 
-  format is also much easier to read as a result of the class format.
+    necessary to figure out how to read data from the dataset. A modular 
+    approach was taken with this project. Users will be able to select a CSV 
+    file to load in. By specifying a class to contain the CSV data it is 
+    possible to run multiple datasets while making only minor modifications to 
+    the code. The format is also much easier to read as a result of the class 
+    format.
 
@@
     by the deep learning framework it was determined to "stand on the shoulders 
-  of giants". Pandas was used to bring CSV data into usable form. After pulling 
-  the data into a single structure it was necessary to split the data into 
-  training and testing data. Again, rather than code that from scratch it was 
-  determined best practice to utilize existing tools.
+    of giants". Pandas was used to bring CSV data into usable form. After 
+    pulling the data into a single structure it was necessary to split the data 
+    into training and testing data. Again, rather than code that from scratch 
+    it was determined best practice to utilize existing tools.
 
     For that endevour scikit-learn was used, specifically the 
-  $train\_test\_split()$ method. As is standard for classification problems the 
-  data was segmented into 80\% training and 20\% testing data. It was then 
-  necessary to place the $class$ label into a data structure for later. For 
-  both the train and test data, associated labels are passed, along with the 
-  data, as tuples. The psuedocode for this section can be found under Algorithm 
-  \ref{alg:input_fn}.
+    $train\_test\_split()$ method. As is standard for classification problems 
+    the data was segmented into 80\% training and 20\% testing data. It was 
+    then necessary to place the $class$ label into a data structure for later. 
+    For both the train and test data, associated labels are passed, along with 
+    the data, as tuples. The psuedocode for this section can be found under 
+    Algorithm \ref{alg:input_fn}.
     %
@@
     %
+
 \subsection{TensorFlow estimator}
@@
     $model\_dir$ for TensorBoard output which will be discussed in section 
-  \ref{sec:tensorboard}, and the $params$ which consist of $feature\_columns$, 
-  $hidden\_units$, and $n\_classes$.
+    \ref{sec:tensorboard}, and the $params$ which consist of 
+    $feature\_columns$, $hidden\_units$, and $n\_classes$.
 
@@
     %
-  Lastly, the estimator requires a return of $EstimatorSpec$. Documentation for 
-  the EstimatorSpec can be found on \href{https://www.tensorflow.org/api_docs/python/tf/estimator/EstimatorSpec}{TensorFlow's website}.
-It is important to note that each of the different $ModeKeys$ requires a different set of parameters for the returned $EstimatorSpec$.
+    Lastly, the estimator requires a return of $EstimatorSpec$. Documentation 
+    for the EstimatorSpec can be found on \href{https://www.tensorflow.org/api_docs/python/tf/estimator/EstimatorSpec}{TensorFlow's website}. It is important to note 
+    that each of the different $ModeKeys$ requires a different set of 
+    parameters for the returned $EstimatorSpec$.
 
@@
     $\textnormal{model.model\_RMSProp}$. For each of the layers that was passed 
-  to it under $params['hidden\_units']$ there is a fully connected layer built 
-  with selu activation. \citet{selu} found with the proper math you can obtain 
-  self-normalizing exponential linear units, meaning they don't require batch 
-  normalization and that is why they were chosen over all of the other 
-  activation functions. There is also the final fully connected layer which has 
-  no activation layer. This final layer aids in determining the classification.
+    to it under $params['hidden\_units']$ there is a fully connected layer 
+    built with selu activation. \citet{selu} found with the proper math you can 
+    obtain self-normalizing exponential linear units, meaning they don't 
+    require batch normalization and that is why they were chosen over all of 
+    the other activation functions. There is also the final fully connected 
+    layer which has no activation layer. This final layer aids in determining 
+    the classification.
 
     During training ModeKeys.TRAIN is called, which specifies RMSProp gradient 
-  descent as our optimizer and then calls $minimize()$. The $minimize()$ method 
-  will automatically compute the gradients and apply them to the variables, but 
-  if you need to tune the network there are additional steps that can be taken 
-  instead:
+    descent as our optimizer and then calls $minimize()$. The $minimize()$ 
+    method will automatically compute the gradients and apply them to the 
+    variables, but if you need to tune the network there are additional steps 
+    that can be taken instead:
     %
@@
     {class Optimizer}. It was not necessary to have that level of fidelity with 
-  this particular dataset, so the base $minimize()$ was all that was necessary.
+    this particular dataset, so the base $minimize()$ was all that was 
+    necessary.
 
-  With $minimize()$ minimizing the loss we are able to make progress towards a 
-  classification. This dataset in particular minimizes loss to near-zero after 
-  just the first episode of 100 training steps as can be seen in Figure \ref{img:loss}.
+    With $minimize()$ minimizing the loss we are able to make progress towards 
+    a classification. This dataset in particular minimizes loss to near-zero 
+    after just the first episode of 100 training steps as can be seen in Figure 
+    \ref{img:loss}.
 
@@
     significant improvements over the initial parameters set so the associated 
-  code was removed from primary operation of the classifier. The file described 
-  would allow for random testing of hyperparameters across any number of 
-  computers. \citet{hypparam} found random search of hyperparameters to be superior to grid search and was the method used while exploring 
-  hyperparameter tuning during this project.
+    code was removed from primary operation of the classifier. The file 
+    described would allow for random testing of hyperparameters across any 
+    number of computers. \citet{hypparam} found random search of 
+    hyperparameters to be superior to grid search and was the method used while 
+    exploring hyperparameter tuning during this project.
 
 \subsection{TensorBoard}\label{sec:tensorboard}
-  One of the other reasons for utilizing TensorFlow is the TensorBoard project. 
-  TensorBoard allows for visualization of various parameters as defined by the 
-  user. Figure \ref{img:acc_smooth} and \ref{img:loss_smooth} are the same results as shown in Figure \ref{img:accuracy} and \ref{img:loss} 
-  respectively. The smooothing helps in understanding what may be going on, 
-  especially in more turbulant graphs. Another benefit is being able to 
-  visualize the graph structure. To use TensorBoard on this project ensure it 
-  was installed with TensorFlow and type 
+    One of the other reasons for utilizing TensorFlow is the TensorBoard 
+    project. TensorBoard allows for visualization of various parameters as 
+    defined by the user. Figure \ref{img:acc_smooth} and \ref{img:loss_smooth} 
+    are the same results as shown in Figure \ref{img:accuracy} and 
+    \ref{img:loss} respectively. The smooothing helps in understanding what may 
+    be going on, especially in more turbulant graphs. Another benefit is being 
+    able to visualize the graph structure. To use TensorBoard on this project 
+    ensure it was installed with TensorFlow and type 
+    %
     \[\textnormal{tensorboard\ -\--logdir\ model}\]
+    %
     and go to the link it provides (by ctrl clicking or copy/paste). 
-
+    %
     \begin{figure}[H]  
-  \caption{Smoothed Accuracy}\label{img:acc_smooth}
     \begin{center}
-  \includegraphics[scale=0.65]{../images/acc}
+    \includegraphics[scale=0.65]{images/acc}
+    \caption{Smoothed accuracy}\label{img:acc_smooth}
     \end{center}
@@
     \begin{figure}[H]  
-  \caption{Smoothed Loss}\label{img:loss_smooth}
     \begin{center}
-  \includegraphics[scale=0.65]{../images/loss}
+    \includegraphics[scale=0.65]{images/loss}
+    \caption{Smoothed loss}\label{img:loss_smooth}
     \end{center}
     \end{figure}
-
+    %
 \newpage
@@
     samples. Other hyperparameters were three fully connected layers with 12 
-  nodes each using selu activation.
-
+    nodes each using selu activation. Increasing hidden layers led to noisier 
+    loss after the large initial drop. The following had no measurable 
+    improvement on the classification accuracy:
+    \begin{itemize}
+        \item Changing from RMSProp to Adagrad
+        \item Changing batch size
+        \item Modified learning rate
+        \item Depth of layers or number of neurons
+    \end{itemize}
+    %
     \begin{figure}[H]  
-  \caption{Accuracy}\label{img:term_acc}
     \begin{center}
-  \includegraphics[scale=0.75]{../images/accuracy_percent_small}
+    \includegraphics[scale=0.735]{images/accuracy_percent_small}
+    \caption{Detailed accuracy}\label{img:term_acc}
     \end{center}
@@
     \begin{figure}[H]  
+    \begin{center}
+    \includegraphics[scale=0.75]{images/Accuracy}
     \caption{Accuracy}\label{img:accuracy}
-  \begin{center}
-  \includegraphics[scale=0.75]{../images/Accuracy}
     \end{center}
@@
     \begin{figure}[H]
+    \begin{center}
+    \includegraphics[scale=0.75]{images/Loss}
     \caption{Loss}\label{img:loss}
-  \begin{center}
-  \includegraphics[scale=0.75]{../images/Loss}
     \end{center}
     \end{figure}
-
-\section{Conclusion}
-
-\section{General formatting instructions}
-\label{gen_inst}
-
-The text must be confined within a rectangle 5.5~inches (33~picas)
-wide and 9~inches (54~picas) long. The left margin is 1.5~inch
-(9~picas).  Use 10~point type with a vertical spacing (leading) of
-11~points.  Times New Roman is the preferred typeface throughout, and
-will be selected for you by default.  Paragraphs are separated by
-\nicefrac{1}{2}~line space (5.5 points), with no indentation.
-
-The paper title should be 17~point, initial caps/lower case, bold,
-centered between two horizontal rules. The top rule should be 4~points
-thick and the bottom rule should be 1~point thick. Allow
-\nicefrac{1}{4}~inch space above and below the title to rules. All
-pages should start at 1~inch (6~picas) from the top of the page.
-
-For the final version, authors' names are set in boldface, and each
-name is centered above the corresponding address. The lead author's
-name is to be listed first (left-most), and the co-authors' names (if
-different address) are set to follow. If there is only one co-author,
-list both author and co-author side by side.
-
-Please pay special attention to the instructions in Section \ref{others}
-regarding figures, tables, acknowledgments, and references.
-
-\section{Headings: first level}
-\label{headings}
-
-All headings should be lower case (except for first word and proper
-nouns), flush left, and bold.
-
-First-level headings should be in 12-point type.
-
-\subsection{Headings: second level}
-
-Second-level headings should be in 10-point type.
-
-\subsubsection{Headings: third level}
-
-Third-level headings should be in 10-point type.
-
-\paragraph{Paragraphs}
-
-There is also a \verb+\paragraph+ command available, which sets the
-heading in bold, flush left, and inline with the text, with the
-heading followed by 1\,em of space.
-
-\section{Citations, figures, tables, references}
-\label{others}
-
-These instructions apply to everyone.
-
-\subsection{Citations within the text}
-
-The \verb+natbib+ package will be loaded for you by default.
-Citations may be author/year or numeric, as long as you maintain
-internal consistency.  As to the format of the references themselves,
-any style is acceptable as long as it is used consistently.
-
-The documentation for \verb+natbib+ may be found at
-\begin{center}
-  \url{http://mirrors.ctan.org/macros/latex/contrib/natbib/natnotes.pdf}
-\end{center}
-Of note is the command \verb+\citet+, which produces citations
-appropriate for use in inline text.  For example,
-\begin{verbatim}
-   \citet{hasselmo} investigated\dots
-\end{verbatim}
-produces
-\begin{quote}
-  Hasselmo, et al.\ (1995) investigated\dots
-\end{quote}
-
-If you wish to load the \verb+natbib+ package with options, you may
-add the following before loading the \verb+nips_2017+ package:
-\begin{verbatim}
-   \PassOptionsToPackage{options}{natbib}
-\end{verbatim}
-
-If \verb+natbib+ clashes with another package you load, you can add
-the optional argument \verb+nonatbib+ when loading the style file:
-\begin{verbatim}
-   \usepackage[nonatbib]{nips_2017}
-\end{verbatim}
-
-As submission is double blind, refer to your own published work in the
-third person. That is, use ``In the previous work of Jones et
-al.\ [4],'' not ``In our previous work [4].'' If you cite your other
-papers that are not widely available (e.g., a journal paper under
-review), use anonymous author names in the citation, e.g., an author
-of the form ``A.\ Anonymous.''
-
-\subsection{Footnotes}
-
-Footnotes should be used sparingly.  If you do require a footnote,
-indicate footnotes with a number\footnote{Sample of the first
-  footnote.} in the text. Place the footnotes at the bottom of the
-page on which they appear.  Precede the footnote with a horizontal
-rule of 2~inches (12~picas).
-
-Note that footnotes are properly typeset \emph{after} punctuation
-marks.\footnote{As in this example.}
-
-\subsection{Figures}
-
-All artwork must be neat, clean, and legible. Lines should be dark
-enough for purposes of reproduction. The figure number and caption
-always appear after the figure. Place one line space before the figure
-caption and one line space after the figure. The figure caption should
-be lower case (except for first word and proper nouns); figures are
-numbered consecutively.
-
-You may use color figures.  However, it is best for the figure
-captions and the paper body to be legible if the paper is printed in
-either black/white or in color.
-\begin{figure}[h]
-  \centering
-  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
-  \caption{Sample figure caption.}
-\end{figure}
-
-\subsection{Tables}
-
-All tables must be centered, neat, clean and legible.  The table
-number and title always appear before the table.  See
-Table~\ref{sample-table}.
-
-Place one line space before the table title, one line space after the
-table title, and one line space after the table. The table title must
-be lower case (except for first word and proper nouns); tables are
-numbered consecutively.
-
-Note that publication-quality tables \emph{do not contain vertical
-  rules.} We strongly suggest the use of the \verb+booktabs+ package,
-which allows for typesetting high-quality, professional tables:
-\begin{center}
-  \url{https://www.ctan.org/pkg/booktabs}
-\end{center}
-This package was used to typeset Table~\ref{sample-table}.
-
-\begin{table}[t]
-  \caption{Sample table title}
-  \label{sample-table}
-  \centering
-  \begin{tabular}{lll}
-    \toprule
-    \multicolumn{2}{c}{Part}                   \\
-    \cmidrule{1-2}
-    Name     & Description     & Size ($\mu$m) \\
-    \midrule
-    Dendrite & Input terminal  & $\sim$100     \\
-    Axon     & Output terminal & $\sim$10      \\
-    Soma     & Cell body       & up to $10^6$  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\section{Final instructions}
-
-Do not change any aspects of the formatting parameters in the style
-files.  In particular, do not modify the width or length of the
-rectangle the text should fit into, and do not change font sizes
-(except perhaps in the \textbf{References} section; see below). Please
-note that pages should be numbered.
-
-\section{Preparing PDF files}
-
-Please prepare submission files with paper size ``US Letter,'' and
-not, for example, ``A4.''
-
-Fonts were the main cause of problems in the past years. Your PDF file
-must only contain Type 1 or Embedded TrueType fonts. Here are a few
-instructions to achieve this.
-
-\begin{itemize}
-
-\item You should directly generate PDF files using \verb+pdflatex+.
-
-\item You can check which fonts a PDF files uses.  In Acrobat Reader,
-  select the menu Files$>$Document Properties$>$Fonts and select Show
-  All Fonts. You can also use the program \verb+pdffonts+ which comes
-  with \verb+xpdf+ and is available out-of-the-box on most Linux
-  machines.
-
-\item The IEEE has recommendations for generating PDF files whose
-  fonts are also acceptable for NIPS. Please see
-  \url{http://www.emfield.org/icuwb2010/downloads/IEEE-PDF-SpecV32.pdf}
-
-\item \verb+xfig+ "patterned" shapes are implemented with bitmap
-  fonts.  Use "solid" shapes instead.
-
-\item The \verb+\bbold+ package almost always uses bitmap fonts.  You
-  should use the equivalent AMS Fonts:
-\begin{verbatim}
-   \usepackage{amsfonts}
-\end{verbatim}
-followed by, e.g., \verb+\mathbb{R}+, \verb+\mathbb{N}+, or
-\verb+\mathbb{C}+ for $\mathbb{R}$, $\mathbb{N}$ or $\mathbb{C}$.  You
-can also use the following workaround for reals, natural and complex:
-\begin{verbatim}
-   \newcommand{\RR}{I\!\!R} %real numbers
-   \newcommand{\Nat}{I\!\!N} %natural numbers
-   \newcommand{\CC}{I\!\!\!\!C} %complex numbers
-\end{verbatim}
-Note that \verb+amsfonts+ is automatically loaded by the
-\verb+amssymb+ package.
-
-\end{itemize}
-
-If your file contains type 3 fonts or non embedded TrueType fonts, we
-will ask you to fix it.
-
-\subsection{Margins in \LaTeX{}}
-
-Most of the margin problems come from figures positioned by hand using
-\verb+\special+ or other commands. We suggest using the command
-\verb+\includegraphics+ from the \verb+graphicx+ package. Always
-specify the figure width as a multiple of the line width as in the
-example below:
-\begin{verbatim}
-   \usepackage[pdftex]{graphicx} ...
-   \includegraphics[width=0.8\linewidth]{myfile.pdf}
-\end{verbatim}
-See Section 4.4 in the graphics bundle documentation
-(\url{http://mirrors.ctan.org/macros/latex/required/graphics/grfguide.pdf})
-
-A number of width problems arise when \LaTeX{} cannot properly
-hyphenate a line. Please give LaTeX hyphenation hints using the
-\verb+\-+ command when necessary.
-
-\subsubsection*{Acknowledgments}
-
-Use unnumbered third level headings for the acknowledgments. All
-acknowledgments go at the end of the paper. Do not include
-acknowledgments in the anonymized submission, only in the final paper.
-
-\section*{References}
-
-References follow the acknowledgments. Use unnumbered first-level
-heading for the references. Any choice of citation style is acceptable
-as long as you are consistent. It is permissible to reduce the font
-size to \verb+small+ (9 point) when listing the references. {\bf
-  Remember that you can go over 8 pages as long as the subsequent ones contain
-  \emph{only} cited references.}
-\medskip
-
-\small
-
-[1] Alexander, J.A.\ \& Mozer, M.C.\ (1995) Template-based algorithms
-for connectionist rule extraction. In G.\ Tesauro, D.S.\ Touretzky and
-T.K.\ Leen (eds.), {\it Advances in Neural Information Processing
-  Systems 7}, pp.\ 609--616. Cambridge, MA: MIT Press.
-
-[2] Bower, J.M.\ \& Beeman, D.\ (1995) {\it The Book of GENESIS:
-  Exploring Realistic Neural Models with the GEneral NEural SImulation
-  System.}  New York: TELOS/Springer--Verlag.
-
-[3] Hasselmo, M.E., Schnell, E.\ \& Barkai, E.\ (1995) Dynamics of
-learning and recall at excitatory recurrent synapses and cholinergic
-modulation in rat hippocampal region CA3. {\it Journal of
-  Neuroscience} {\bf 15}(7):5249-5262.
-
-% [4] Bergstra, J.\ \& Bengio, J.\ (2012) Random Search for Hyper-Parameter 
-% Optimization. {\it Journal of Machine Learning Research 13} pp.\ 281-305.
+    %
+\section{Conclusion and future work}
+    In conclusion, this particular dataset ended up being relatively simple to 
+    classify with modern methods. The original paper reported the exact same 
+    accuracy of 97.8\% using a Gaussian Hellinger Very Fast Decision Tree. Room 
+    for improvement could be a better interface for the CSV files and possible 
+    command line arguments. Additionally, the accuracy would occasionally break 
+    98\%, but was rare. There is possible room for improvement on the 
+    hyperparameters to increase the accuracy consistently beyond 98\%. The loss 
+    function dropped off almost immediately, so it could probably deal with 
+    fewer hidden layers and/or neurons. Another possible improvement may be 
+    adding extra feature layers that are extrapolated from the pulsars (or 
+    possibly non-pulsars).
 

### 2018-04-23 main.py

@@ -35,7 +35,7 @@ _HIDDEN_LAYERS = [_NODES_PER_LAYER]*_LAYERS
 def main(argv):
     # Clears all previous models
     for name in glob.glob('model_*'):
-      shutil.rmtree(name)
+        shutil.rmtree(name)
     
     runs = 1
     try:

### 2018-04-23 main.py
Forgot I had changed the batch size while testing shutil.rmtree()...fixed. Done.

@@ -15,7 +15,7 @@ from network import run_network
 _NUM_ELEMENTS = 17898
 _TEST_PERCENTAGE = 0.2
 _TRAIN = int(_NUM_ELEMENTS*(1-_TEST_PERCENTAGE))
-_BATCH_SIZE = max(int(_TRAIN*.001), 1)
+_BATCH_SIZE = max(int(_TRAIN*.1), 1)
 _MODEL = model_RMSProp
 
 # Create a CSV object
